---
title: "Report Example"
author: "Thomas Sol Dourdin"
date: "`r Sys.Date()`"
format: pdf
editor: source
---


# First title
## Second title

| Now I can write some texte before integrating **code**:
```{r}
dim(iris)
```

| Depending on the specified *options*, we can see the code without the result...
```{r}
#| eval: false
dim(iris)
```

| ...or we can see the result without the code.
```{r}
#|  echo: false
dim(iris)
```

| Something very useful is that we can also integrate inline code, for instance: `r 2+2`.

| Now, if you have an executable script (creating object, displaying nothing) from which you want to make a report. You have to specify:

```{r setup}
#| warning: false
#| message: false

library(here)
source(here("R", "NoFunctions.R"))
```


| Doing that, all the objects produced by the referenced script are available to Rmarkdown. 
| Consequently, we can display the plots directly from the original script

```{r}
#| fig-cap: "Plot 1"
#| fig-width: 5.5
#| echo: false
p
```

```{r}
#| echo: false
pvalue <- Res[["Pr(>F)"]][1]
```

| But we can also use the inline code to give some statistics or information from the script, so it will change automatically if you modify the script. For instance, we ran an ANOVA and thanks to the inline code, we can automatically report the p-value (`r pvalue`). Thus, if you change something in the data and re-run the ANOVA, the p-value will be automatically updated in your report.

<!-- And finally, we can include comments within the doc. The comments do not appear in the rendered document. -->