---
title: "Example of a Quarto Article"
author: "Thomas Sol Dourdin^1,2^, Jean-Baptiste Ledoux^2^"
format:
  docx:
    reference-doc: mystyles.docx
    df_print: "paged"
    number_sections: true
    fig_caption: true
bibliography: library.bib
csl: ieee.csl
---


```{r setup}
#| include: FALSE
#| warning: false
#| message: false
knitr::opts_chunk$set(echo = TRUE)

library(here)
source(here("R", "NoFunctions.R"))

```

1. Littoral Environnement et Sociétés (LIENSs), UMR 7266 CNRS – La Rochelle Université, 2 rue Olympe de Gouges, 17000 La Rochelle, France.
2. CIIMAR/CIMAR LA, Centro Interdisciplinar de Investigação Marinha e Ambiental, Universidade do Porto, Terminal de Cruzeiros do Porto de Leixões, 4450-208 Matosinhos, Portugal.

<br>

# Introduction

|  Cephalopods are becoming promising model systems in ecotoxicology, for biomonitoring [@Ajala2022] as well as experimental studies [@Penicaud2017;@Garca-Flores2025]. They are also a meal really loved by Iberian people: Portuguese and Spanish. For instance, one of the best way to cook octopus is the *pulpo a la gallega*.

<br>

# Materials and Methods

## Description of the biological material

| The best octopuses are found directly on the dock of fishing harbours. Ask to fishers if they cought some, but do it kindly because they are sensible guys.

<br>

## Cooking recipe

| Too long to details it here, sorry... Instead, focus on bivalves from Sine Saloum, easier to cook.

<br>

# Results

| The length of individuals found in different stations are displayed in the Figure 1.

```{r}
#| label: Figure1
#| fig-cap: "Figure 1: What a beautiful plot!"
#| fig-width: 6
#| fig-height: 4
#| fig-dpi: 500
#| echo: false
#| warning: false
#| message: false

p
```

<br>

| But, it is also noteworthy that the total number of samples is `r nrow(data)`.

| Moreover, if we want, we can use the packages *flextable* and *ftExtra* to include the data (first 10 rows) as a beautiful table:

```{r}
#| label: Table1
#| echo: false
#| warning: false
#| message: false


library(knitr)
library(flextable)
library(ftExtra)
library(dplyr)

table1 <- data
table <- table1[1:10,]

flextable(table) %>%
  theme_vanilla() %>%
  padding(padding=2) %>%
  fontsize(size=8, part = "header") %>%
  fontsize(size=8, part="body") %>%
  align(align="left", part="all") %>%
  set_table_properties(layout = "autofit", width=1) %>%
  set_caption("Table 1: Sequencing statistics for newly hatched juveniles. GeT-PlaGe sample code is used for the labelling of reads in the European Nucleotide Archive repository. R1 GC% and R2 GC% are percent GC content on the forward and reverse reads, respectively.")
```

<!-- And finally, we can include comments within the doc. The comments do not appear in the rendered document. -->

\newpage
# References